Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/related_work.tex

\section{Related Work}

\begin{itemize}
  \item Hyperparameter optimization: random, bayesian opt, bandit methods
  \item distillation techniques
  \item post-training compression techniques
  \item group sparsity, non-parametric neural networks
  \item training dynamics paper: first overfitting and then randomization?, \gl{Here is the ref, if you can introduce it in the flow \cite{Shwartz-Ziv2017}}
\end{itemize}

>>>>

%!TEX root=paper.tex
\section{Related Work}

\begin{itemize}
  \item Other techniques for choosing network size (e.g., hyperparmeter optimization) -- manual effort vs optimal techniques -- people actually don't treat network size as a hyperparameter;  we do!  Also brute force techniques~\cite{nvidia-paper-xxx}
  \item distillation techniques -- train a big net, then train a smaller net from it 
  \item post-training compression techniques -- brain damage , 
  \item group sparsity e.g., \cite{Scardapane2017} and non-parametric neural networks -- 
  \item training dynamics paper: first overfitting and then randomization?, \gl{Here is the ref, if you can introduce it in the flow \cite{Shwartz-Ziv2017}}
\end{itemize}
